\section*{Introduction}

Distributed systems take many forms, and many of the best known and most widely
used computer systems are as prevalent as they are because of their distributed
nature. This course unit introduces some of the essential concepts underlying
distributed systems.

Students are guided into an exploration of exemplar distributed applications
(such as the web, email, file sharing and multi-user gaming ) and, through these
exemplars, are introduced to the basic concepts that underpin modern distributed
computing.

Recurring themes will include how distributed systems offer transparencies of
various kinds and how they must contend with a range of complex issues to
achieve that.

We also look at how massive distribution enables high-performance computing, how
service abstractions in the web enable business-to-business integration and how
the web of hyperlinked documents is changing into a richer web of data.

\section*{Aims}

This course unit aims to provide students with a basic understanding of
distributed computing, drawing on their general experience as users of
distributed applications to inform the discovery, description and classification
of fundamental concepts in distributed systems.

This course unit builds on the knowledge gained by students in COMP10120: The
First Year Team Project course unit and aims to equip them better to benefit
from more technically-demanding course units in second and third years (in
particular, the course units on Computer Networks, Distributed Computing and
Mobile Systems).

After a brief introduction that contrasts the distributed view of computing with
the centralized one presented in other course units, the course unit progresses
by studying a few exemplar distributed applications, one by one. Each exemplar
application is chosen with a view to illustrating issues and challenges arising
in distributed systems.

After each dissection of an exemplar application, time is taken to make
explicit, in a more systematic way, some of the basic principles involved, how
tools and techniques have been developed that enforce those principles, and how
these tools and techniques both give rise and presuppose the distributed
computing infrastructures that pervade modern computing.

\section*{Additional reading}

\subsection*{Distributed systems: principles and paradigms (2nd edition)}
\begin{tabular}{l l}
	Author: & Tanenbaum, Andrew S. and Maarten van Steen\\
	ISBN: & 0136135536\\
	Publisher: & Pearson / Prentice Hall\\
	Edition: & 2nd\\
	Year: & 2007\\
\end{tabular}